\textsf{Are frontier models superhuman chemists?}

### 2024-03-11 src/tex/ms.tex
Update src/tex/ms.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

\subparagraph{Functional materials and nano-materials}
The questions are gathered from a seminar conducted at the University of Jena, delving into topics concerning functional materials and nano-materials, exploring their properties and applications.

>>>>

\subparagraph{Functional materials and nano-materials}
The questions are gathered from a seminar course conducted at the University of Jena, delving into topics concerning functional materials and nano-materials, exploring their properties and applications.
